### 2017-04-14 sections/math.tex
Update on Overleaf.

Singular value decomposition (SVD) \cite{Baker2005, Kalman1996} is based on a theorem from linear algebra which says that a rectangular matrix $\mtrx{A} \in \mathbb{R}^{m \times n}$ can be decomposed into the product of three matrices - an orthogonal matrix $\mtrx{U} \in \mathbb{R}^{m \times m}$, a diagonal
matrix $\mtrx{S} \in \mathbb{R}^{m \times n}$, and the transpose of an orthogonal matrix $\mtrx{V} \in \mathbb{R}^{n \times n}$:

@@

\subsection{Randomized SVD}
In \cite{Holmes2007, Halko2011, Candes2011, Woolfe2008, Martinsson2011} are described randomized algorithms for constructing approximate matrix factorizations. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

>>>>

Singular value decomposition (SVD) \cite{Baker2005, Kalman1996, Golub1996} is based on a theorem from linear algebra which says that a rectangular matrix $\mtrx{A} \in \mathbb{R}^{m \times n}$ can be decomposed into the product of three matrices - an orthogonal matrix $\mtrx{U} \in \mathbb{R}^{m \times m}$, a diagonal
matrix $\mtrx{S} \in \mathbb{R}^{m \times n}$, and the transpose of an orthogonal matrix $\mtrx{V} \in \mathbb{R}^{n \times n}$:

@@

\subsection{Randomized SVD}
In \cite{Holmes2007, Candes2011, Woolfe2008, Martinsson2011} are described randomized algorithms for constructing approximate matrix factorizations. Their main purpose is to accelerate calculations of matrix decompositions which tend to be very slow for large data sets.

% TODO: add citation with description of algorithm: \cite{Halko2011}
